### 2017-10-13 Gruba/01-intro.tex

Central to user behavior modeling, is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

>>>>

Central to user behavior modeling is the need to choose the right granularity of model (i.e., how many users share one model), as well as the variety of features to be utilized for differentiating users.
Already, there exist work of building a single model for all the users \cite{IEEEexample:conf/wsdm/FengW13,IEEEexample:conf/ijcai/ZhangLTCL13,IEEEexample:journals/tkdd/ZhangTLLX15}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.
